---
title: "Picture perception analysis"
format: html
---

```{r}
# install.packages("emmeans")
# install.packages("brms")
# install.packages("tidybayes")
# install.packages("broom.mixed")
# install.packages("psych")
# install.packages("lavaan")
# install.packages("gridExtra")

library(here)
library(tidyverse)
library(lme4)
library(emmeans)
library(brms)
library(tidybayes)
library(broom.mixed)
library(psych)
library(lavaan)
library(dplyr)
library(ggplot2)
library(gridExtra)
```

```{r}
d <- read_csv(here("data","kisumu_vocab_data.csv"))
```
# visualization

```{r}
ms <- d |>
  group_by(child, condition, age) |>
  summarise(accuracy = mean(accuracy))
```

Age distribution. 

```{r}
ggplot(ms, aes(x = age)) + 
  geom_histogram(binwidth = .5)
```



```{r}

ms <- d |>
  group_by(child, condition_label, age) |>
  summarise(accuracy = mean(accuracy)) 

mss <- ms |>
  mutate(age_group = as.factor(floor(age))) |>
  group_by(condition_label, age_group) |>
  summarise(se = sd(accuracy) / sqrt(n()),
            ci = se * qt(.975, n() - 1),
            accuracy = mean(accuracy)) |>
  mutate(age = as.numeric(as.character(age_group)) + .5, 
         condition_label = fct_relevel(condition_label, "Object", "Photo", "Cartoon", "B&W Drawing"))

kisumu_plot <- ggplot(ms, aes(x = age, y = accuracy, col = condition_label)) + 
  geom_pointrange(data = mss,
                  aes(ymin = accuracy - ci, ymax = accuracy + ci), 
                  position = position_dodge(width = .2)) +
  # geom_line(data = mss, aes(y = accuracy), position = position_dodge(width = .2)) +
  geom_jitter(alpha = .2, height = .01, width = 0) + 
  geom_hline(yintercept = .25, lty = 2) + 
  geom_smooth(method = "loess", span = 1, alpha = .2) + 
  scale_color_manual(name = "Condition", 
                     values = c(
                    "B&W Drawing" = "#ABDDA4",
                    "Cartoon" = "#66C2A5" ,
                    "Photo" = "#3288BD" ,
                    "Object" = "#5E4FA2" )) + 
  ylim(0, 1)  + 
  # ggthemes::scale_color_solarized(name="Condition") + 
  ylab("Accuracy") +
  xlab("Age (Years)") + 
  theme(legend.position = "bottom") +
  theme_classic()

```

# Preregistered analyses

Let's set objects to the reference level. We'll also center age for interpretability. 

These models fail to converge pretty substantially with the maximal preregistered random effects structure. 

Also, good practice to center age to make the intercept more interpretable. (Helps with convergence too often).

```{r}
d$condition <- relevel(factor(d$condition), ref = "obj")
d$age_centered <- scale(d$age, scale = FALSE, center = TRUE)[,1]
```

First model. 

```{r}
mod <- glmer(accuracy ~ condition + (condition | child) + (condition | target_word),
             data = d, family = "binomial")
summary(mod)
```

We remove random effects following our general lab protocol. This results in crossed intercepts but no slopes. 

```{r}
mod_pruned <- glmer(accuracy ~ condition + (1 | child) + (1 | target_word), 
             data = d, family = "binomial")
summary(mod_pruned)


#get confidence intervals
cc <- confint(mod_pruned,parm="beta_",method="Wald")
ctab <- cbind(est=fixef(mod_pruned),cc)
rtab <- exp(ctab)
print(rtab,digits=3)
```

This shows pretty clearly that age is worse.

We fit the same preregistered model with age. 

```{r}
mod_age <- glmer(accuracy ~ condition * age_centered + 
                   (condition | child) + 
                   (condition * age_centered | target_word), 
              data = d, family = "binomial")
summary(mod_age)
```

Again we prune - random slopes are singular, but the intercepts converge. 

```{r}
mod_age_pruned <- glmer(accuracy ~ condition * age_centered + 
                   (1 | child) + 
                   (1 | target_word), 
              data = d, family = "binomial")
summary(mod_age_pruned)

#get confidence intervals
cc_age <- confint(mod_age_pruned,parm="beta_",method="Wald")
ctab_age <- cbind(est=fixef(mod_age_pruned),cc_age)
rtab_age <- exp(ctab_age)
print(rtab_age,digits=3)
```

You also get a pretty clear age interaction: BW is worse and grows more slowly. 

The other conditions are definitely better and don't appear to be distinguishable from object. 

# More viz

Because this is a within-subjects analysis, we can look at the effect for each kid by basic subtraction.

```{r}
ms <- ms |>
  group_by(child) |>
  mutate(effect = accuracy - accuracy[condition == "obj"])

ggplot(filter(ms, condition != "obj"),
       aes(x = age, y = effect)) + 
  geom_jitter(alpha = .3, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  geom_hline(yintercept = 0, lty = 2) + 
  facet_wrap(~condition) + 
  ylab("Accuracy compared to object") +
  xlab("Age (months)")
```
This confirms our analysis above. 

Now running exploratory Bayesian analyses with full models - first in pre-registered model without age
```{r}
bayes_mod <- brm(formula = accuracy ~ condition + (condition | child) + (condition | target_word),
                 family=bernoulli(link="logit"), data = d, seed = 1)

joint_tests(bayes_mod)

#no effect of condition in model without age

```
Get posterior estimates + 95% credible intervals

```{r}
bayes_mod %>%
  as_draws_df() %>%
  select(starts_with("b_")) %>% 
  mutate(obj = b_Intercept, 
         bw = b_Intercept + b_conditionbw, 
     	   cartoon = b_Intercept + b_conditioncartoon,
         photo = b_Intercept + b_conditionphoto) %>%
  select(obj, photo, cartoon, bw) %>%
  mean_hdi() %>%
  pivot_longer(cols = -c(.width:.interval),
               names_to = "index",
               values_to = "value") %>% 
  select(index, value) %>% 
  mutate(index = ifelse(str_detect(index, fixed(".")), index, str_c(index, ".mean"))) %>% 
  separate(index, into = c("parameter", "type"), sep = "\\.") %>% 
  pivot_wider(names_from = type, 
              values_from = value) %>%
  mutate_at(vars(2:4), plogis)

emmeans_bayes_mod <- bayes_mod%>% emmeans(specs = pairwise~condition)
summary(emmeans_bayes_mod)
```

Second, running exploratory Bayesian analyses with full model with age
```{r}
bayes_mod_age <- brm(formula = accuracy ~ condition * age_centered + 
                   (condition | child) + 
                   (condition * age_centered | target_word),
                 family=bernoulli(link="logit"), data = d, seed = 1)

joint_tests(bayes_mod_age)

#main effect of age, no effect of condition

#model term             df1 df2 F.ratio  Chisq p.value
#condition                3 Inf   1.536  4.608  0.2027
#age_centered             1 Inf  15.569 15.569  0.0001
#condition:age_centered   3 Inf   1.594  4.782  0.1886
```

Get posterior estimates + 95% credible intervals
```{r}
bayes_mod_age %>%
  as_draws_df() %>%
  select(starts_with("b_")) %>% 
  mutate(obj = b_Intercept, 
         bw = b_Intercept + b_conditionbw, 
     	   cartoon = b_Intercept + b_conditioncartoon,
         photo = b_Intercept + b_conditionphoto) %>%
  select(obj, photo, cartoon, bw) %>%
  mean_hdi() %>%
  pivot_longer(cols = -c(.width:.interval),
               names_to = "index",
               values_to = "value") %>% 
  select(index, value) %>% 
  mutate(index = ifelse(str_detect(index, fixed(".")), index, str_c(index, ".mean"))) %>% 
  separate(index, into = c("parameter", "type"), sep = "\\.") %>% 
  pivot_wider(names_from = type, 
              values_from = value) %>%
  mutate_at(vars(2:4), plogis)

bayes_mod_age%>% emmeans(specs = pairwise~condition)
```

Run Bayesian analyses on pruned model without age

```{r}
bayes_mod_pruned <- brm(formula = accuracy ~ condition + (1 | child) + (1 | target_word),
                 family=bernoulli(link="logit"), data = d, seed = 1)

summary(bayes_mod_pruned)

joint_tests(bayes_mod_pruned)

#effect of condition
#model term df1 df2 F.ratio Chisq p.value
#condition    3 Inf   2.654 7.962  0.0468
```

Get posterior estimates and 95% credible intervals

```{r}
bayes_mod_pruned %>%
  as_draws_df() %>%
  select(starts_with("b_")) %>% 
  mutate(obj = b_Intercept, 
         bw = b_Intercept + b_conditionbw, 
     	   cartoon = b_Intercept + b_conditioncartoon,
         photo = b_Intercept + b_conditionphoto) %>%
  select(obj, photo, cartoon, bw) %>%
  mean_hdi() %>%
  pivot_longer(cols = -c(.width:.interval),
               names_to = "index",
               values_to = "value") %>% 
  select(index, value) %>% 
  mutate(index = ifelse(str_detect(index, fixed(".")), index, str_c(index, ".mean"))) %>% 
  separate(index, into = c("parameter", "type"), sep = "\\.") %>% 
  pivot_wider(names_from = type, 
              values_from = value) %>%
  mutate_at(vars(2:4), plogis)

bayes_mod_pruned%>% emmeans(specs = pairwise~condition)
```

Run Bayesian analyses on pruned model with age

```{r}
bayes_mod_age_pruned <-  brm(formula = accuracy ~ condition * age_centered + (1 | child) + (1 | target_word), 
                              family=bernoulli(link="logit"), data = d, seed = 1)

summary(bayes_mod_age_pruned)

joint_tests(bayes_mod_age_pruned)

# model term             df1 df2 F.ratio   Chisq p.value
# condition                3 Inf   3.455  10.365  0.0157
# age_centered             1 Inf 100.641 100.641  <.0001
# condition:age_centered   3 Inf   5.167  15.501  0.0014
```

Get posterior estimates and 95% credible intervals

```{r}
bayes_mod_age_pruned %>%
  as_draws_df() %>%
  select(starts_with("b_")) %>% 
  mutate(obj = b_Intercept, 
         bw = b_Intercept + b_conditionbw, 
     	   cartoon = b_Intercept + b_conditioncartoon,
         photo = b_Intercept + b_conditionphoto) %>%
  select(obj, photo, cartoon, bw) %>%
  mean_hdi() %>%
  pivot_longer(cols = -c(.width:.interval),
               names_to = "index",
               values_to = "value") %>% 
  select(index, value) %>% 
  mutate(index = ifelse(str_detect(index, fixed(".")), index, str_c(index, ".mean"))) %>% 
  separate(index, into = c("parameter", "type"), sep = "\\.") %>% 
  pivot_wider(names_from = type, 
              values_from = value) %>%
  mutate_at(vars(2:4), plogis)

bayes_mod_age_pruned%>% emmeans(specs = pairwise~condition)
```

Similar analyses with US data - start by visualizing the data

```{r}

us_d <- read_csv(here("data","us_vocab_data.csv"))

us_ms <- us_d |>
  group_by(child, condition_label, age) |>
  summarise(accuracy = mean(accuracy)) 

us_mss <- us_ms |>
  mutate(age_group = as.factor(floor(age))) |>
  group_by(condition_label, age_group) |>
  summarise(se = sd(accuracy) / sqrt(n()),
            ci = se * qt(.975, n() - 1),
            accuracy = mean(accuracy)) |>
  mutate(age = as.numeric(as.character(age_group)) + .5, 
         condition_label = fct_relevel(condition_label, "Object", "Photo", "Cartoon", "B&W Drawing"))

us_plot <- ggplot(us_ms, aes(x = age, y = accuracy, col = condition_label)) + 
  geom_pointrange(data = us_mss,
                  aes(ymin = accuracy - ci, ymax = accuracy + ci), 
                  position = position_dodge(width = .2)) +
  # geom_line(data = mss, aes(y = accuracy), position = position_dodge(width = .2)) +
  geom_jitter(alpha = .2, height = .01, width = 0) + 
  geom_hline(yintercept = .25, lty = 2) + 
  geom_smooth(method = "loess", span = 1, alpha = .2) + 
  scale_color_manual(name = "Condition", 
                     values = c(
                    "B&W Drawing" = "#ABDDA4",
                    "Cartoon" = "#66C2A5" ,
                    "Photo" = "#3288BD" ,
                    "Object" = "#5E4FA2" )) + 
  # ggthemes::scale_color_solarized(name="Condition") + 
    ylim(0, 1)  +
  ylab("Accuracy") +
  xlab("Age (Years)") + 
  theme(legend.position = "bottom") +
  theme_classic()

```

Pre-registered analysis - full model
```{r}
us_d$condition <- relevel(factor(us_d$condition), ref = "obj")
us_d$age_centered <- scale(us_d$age, scale = FALSE, center = TRUE)[,1]

us_mod <- glmer(accuracy ~ condition + (condition | child) + (condition | target_word),
             data = us_d, family = "binomial")
summary(us_mod)
#failure to converge
```

Full model failed to converge - let's try a pruned model

```{r}
us_mod_pruned <- glmer(accuracy ~ condition + (1 | child) + (1 | target_word), 
             data = us_d, family = "binomial")
summary(us_mod_pruned)
#marginal effect of object vs. bw, p = 0.0873

#get confidence intervals
cc <- confint(us_mod_pruned,parm="beta_",method="Wald")
ctab <- cbind(est=fixef(us_mod_pruned),cc)
rtab <- exp(ctab)
print(rtab,digits=3)
```

Let's try a full model with age

```{r}
us_mod_age <- glmer(accuracy ~ condition * age_centered + 
                   (condition | child) + 
                   (condition * age_centered | target_word), 
              data = us_d, family = "binomial")
summary(us_mod_age)
```
Full model fails to converge - let's try pruned model with age

```{r}
us_mod_age_pruned <- glmer(accuracy ~ condition * age_centered + 
                   (1 | child) + 
                   (1 | target_word), 
              data = us_d, family = "binomial")
summary(us_mod_age_pruned)
#main effect of age, marginal effect of object vs. black-and-white line drawings

#get confidence intervals
cc <- confint(us_mod_age_pruned,parm="beta_",method="Wald")
ctab <- cbind(est=fixef(us_mod_age_pruned),cc)
rtab <- exp(ctab)
print(rtab,digits=3)
```

Let's try some exploratory Bayesian models on the US data - first on the full model without age

```{r}
us_bayes_mod <- brm(formula = accuracy ~ condition + (condition | child) + (condition | target_word),
                 family=bernoulli(link="logit"), data = us_d, seed = 1)

joint_tests(us_bayes_mod)

#no effect of condition in model without age
#model term df1 df2 F.ratio Chisq p.value
# condition    3 Inf   1.315 3.945  0.2675

```

Get posterior estimates + 95% credible intervals

```{r}

us_bayes_mod %>%
  as_draws_df() %>%
  select(starts_with("b_")) %>% 
  mutate(obj = b_Intercept, 
         bw = b_Intercept + b_conditionbw, 
     	   cartoon = b_Intercept + b_conditioncartoon,
         photo = b_Intercept + b_conditionphoto) %>%
  select(obj, photo, cartoon, bw) %>%
  mean_hdi() %>%
  pivot_longer(cols = -c(.width:.interval),
               names_to = "index",
               values_to = "value") %>% 
  select(index, value) %>% 
  mutate(index = ifelse(str_detect(index, fixed(".")), index, str_c(index, ".mean"))) %>% 
  separate(index, into = c("parameter", "type"), sep = "\\.") %>% 
  pivot_wider(names_from = type, 
              values_from = value) %>%
  mutate_at(vars(2:4), plogis)

emmeans_us_bayes_mod <- us_bayes_mod%>% emmeans(specs = pairwise~condition)
summary(emmeans_us_bayes_mod)
```
Now an exploratory Bayesian model on the US data, including age

```{r}
us_bayes_mod_age <- brm(formula = accuracy ~ condition * age_centered + 
                   (condition | child) + 
                   (condition * age_centered | target_word),
                 family=bernoulli(link="logit"), data = us_d, seed = 1)

joint_tests(us_bayes_mod_age)

#nothing is significant - age is marginal
# model term             df1 df2 F.ratio Chisq p.value 
# condition                3 Inf   1.396 4.188  0.2419
# age_centered             1 Inf   3.546 3.546  0.0597
# condition:age_centered   3 Inf   0.089 0.267  0.9663
```

Get posterior estimates + 95% credible intervals

```{r}
us_bayes_mod_age %>%
  as_draws_df() %>%
  select(starts_with("b_")) %>% 
  mutate(obj = b_Intercept, 
         bw = b_Intercept + b_conditionbw, 
     	   cartoon = b_Intercept + b_conditioncartoon,
         photo = b_Intercept + b_conditionphoto) %>%
  select(obj, photo, cartoon, bw) %>%
  mean_hdi() %>%
  pivot_longer(cols = -c(.width:.interval),
               names_to = "index",
               values_to = "value") %>% 
  select(index, value) %>% 
  mutate(index = ifelse(str_detect(index, fixed(".")), index, str_c(index, ".mean"))) %>% 
  separate(index, into = c("parameter", "type"), sep = "\\.") %>% 
  pivot_wider(names_from = type, 
              values_from = value) %>%
  mutate_at(vars(2:4), plogis)

emmeans_us_bayes_mod_age <- us_bayes_mod_age%>% emmeans(specs = pairwise~condition)
summary(emmeans_us_bayes_mod_age)
```
Exploratory comparisons across both cultures

```{r}
full_d <- read_csv(here("data","full_vocab_data.csv"))

full_d$condition <- relevel(factor(full_d$condition), ref = "obj")
full_d$age_centered <- scale(full_d$age, scale = FALSE, center = TRUE)[,1]
```

Let's try a full model with interactions between context, condition, and age

```{r}
full_mod_age <- glmer(accuracy ~ context*condition * age_centered + 
                   (condition | child) + 
                   (condition * age_centered | target_word), 
              data = full_d, family = "binomial")
summary(full_mod_age)
#fails to converge
```

Let's try a pruned model with interactions between context, condition, and age

```{r}
full_mod_age_pruned <- glmer(accuracy ~ context*condition * age_centered + 
                   (1 | child) + 
                   (1 | target_word), 
              data = full_d, family = "binomial")
summary(full_mod_age_pruned)

#main effect of context and age
#interaction between bw x age
```
Bayesian full model with interactions between context, condition, and age?

```{r}
full_bayes_mod_age <- brm(formula = accuracy ~ context * condition * age_centered + 
                   (condition | child) + 
                   (condition * age_centered | target_word),
                 family=bernoulli(link="logit"), data = full_d, seed = 1)

joint_tests(full_bayes_mod_age)

# model term                     df1 df2 F.ratio  Chisq p.value
 #context                          1 Inf  47.261 47.261  <.0001
 #condition                        3 Inf   0.561  1.683  0.6409
 #age_centered                     1 Inf   9.889  9.889  0.0017
# context:condition                3 Inf   0.044  0.132  0.9877
# context:age_centered             1 Inf   0.047  0.047  0.8289
 #condition:age_centered           3 Inf   0.087  0.261  0.9673
 #context:condition:age_centered   3 Inf   0.476  1.428  0.6988

#main effect of context and age
```

More data viz - item effects

```{r}

us_ms <- us_ms |>
  group_by(child) |>
  mutate(effect = accuracy - accuracy[condition == "obj"])

ggplot(filter(us_ms, condition != "obj"),
       aes(x = age, y = effect)) + 
  geom_jitter(alpha = .3, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  geom_hline(yintercept = 0, lty = 2) + 
  facet_wrap(~condition) + 
  ylab("Accuracy compared to object") +
  xlab("Age (months)")

```

Kenya item effects plot

```{r}
msi <- d |>
  group_by(condition_label, target_word) |>
  summarise(mean_accuracy = mean(accuracy, na.rm=TRUE),
            ci.lower = binom::binom.confint(sum(accuracy), n = n(), method = "bayes")$lower,
            ci.upper = binom::binom.confint(sum(accuracy), n = n(), method = "bayes")$upper) |>
  ungroup() |>
  mutate(target_word = fct_reorder(target_word, mean_accuracy , .fun = median, .desc=TRUE))

plot <- ggplot(msi,
       aes(x = target_word, y = mean_accuracy , col = condition_label)) + 
  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
                  position = position_dodge(width = .4)) + 
  geom_hline(yintercept = .25, lty = 2)+ 
  geom_line() + 
  # coord_flip() + 
  scale_color_manual(name = "Condition", 
                     values = c(
                    "B&W Drawing" = "#ABDDA4",
                    "Cartoon" = "#66C2A5" ,
                    "Photo" = "#3288BD" ,
                    "Object" = "#5E4FA2" )) + 
# ggthemes::scale_color_solarized(name = "Condition") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  xlab("Item") +
  ylab("Accuracy") +
  theme(legend.position = "bottom") +
  theme(panel.background = element_rect(fill = "white")) +
  theme(axis.line.x.bottom=element_line(color="black")) +
  theme(axis.line.y = element_line(color = "black"))

plot
```

US item effects plot

```{r}
us_msi <- us_d |>
  group_by(condition_label, target_word) |>
  summarise(mean_accuracy = mean(accuracy, na.rm=TRUE),
            ci.lower = binom::binom.confint(sum(accuracy), n = n(), method = "bayes")$lower,
            ci.upper = binom::binom.confint(sum(accuracy), n = n(), method = "bayes")$upper) |>
  ungroup() |>
  mutate(target_word = fct_reorder(target_word, mean_accuracy , .fun = median, .desc=TRUE))

us_plot <- ggplot(us_msi,
       aes(x = target_word, y = mean_accuracy , col = condition_label)) + 
  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
                  position = position_dodge(width = .4)) + 
  geom_hline(yintercept = .25, lty = 2)+ 
  geom_line() + 
  # coord_flip() + 
  scale_color_manual(name = "Condition", 
                     values = c(
                    "B&W Drawing" = "#ABDDA4",
                    "Cartoon" = "#66C2A5" ,
                    "Photo" = "#3288BD" ,
                    "Object" = "#5E4FA2" )) + 
# ggthemes::scale_color_solarized(name = "Condition") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  xlab("Item") +
  ylab("Accuracy") +
  theme(legend.position = "bottom") +
  theme(panel.background = element_rect(fill = "white")) +
  theme(axis.line.x.bottom=element_line(color="black")) +
  theme(axis.line.y = element_line(color = "black")) +
  expand_limits(y=0)

us_plot
```

Clean error analysis data

```{r}
error_d <- read_csv(here("data","error_analyses.csv"))
error_d$condition <- relevel(factor(error_d$condition), ref = "obj")
error_d$age_centered <- scale(error_d$age, scale = FALSE, center = TRUE)[,1]

error_d <- error_d %>% 
              mutate(rounded_age = factor(round(age))) %>% # bin age in two ways 
              mutate(floored_age = factor(floor(age))) %>%
              mutate(response_type = fct_recode(response_type, # also recode response type
                                   "near" = "Near Distractor",
                                   "far" = "Random",
                                   "target" = "Target")) %>%
              mutate(response_type = factor(response_type,
                                            levels = c("far", "near","target"),
                                            ordered = TRUE)) %>%
              mutate(condition = fct_recode(factor(condition), # recode condition and set levels
                                 "b&w" = "bw",
                                 "object" = "obj",
                                 "photo" = "photo",
                                 "cartoon" = "cartoon")) %>% 
              mutate(condition = factor(condition,
                                        levels = c("object", "photo","cartoon", "b&w"),
                                        ordered = FALSE))

agg <-group_by(error_d, context)
kenya <-subset(agg, context == "kenya")
us <-subset(agg, context == "usa")

kenya_errors <- kenya %>%
    filter(response_type %in% c("near","far")) %>% 
    mutate(is_far = response_type=="far")

us_errors <- us %>%
    filter(response_type %in% c("near","far")) %>% 
    mutate(is_far = response_type=="far")
```

Attempt frequentist full model of Kenya error analysis without age (it won't converge)

```{r}
freq_kenya_error_mod <- glmer(is_far ~ condition + (condition | child) + (condition | target_word),
              data = kenya_errors, family = "binomial")
summary(freq_kenya_error_mod)
```

Let's try a pruned model

```{r}
freq_kenya_error_mod_pruned <- glmer(is_far ~ condition + (1 | child) + (1| target_word),
              data = kenya_errors, family = "binomial")
summary(freq_kenya_error_mod_pruned)

#more far errors in all three picture condiitons, relative to object condition - cool!

#get confidence intervals
cc <- confint(freq_kenya_error_mod_pruned,parm="beta_",method="Wald")
ctab <- cbind(est=fixef(freq_kenya_error_mod_pruned),cc)
rtab <- exp(ctab)
print(rtab,digits=3)
```
Now add age into the frequentist model for Kenya data (it won't converge)

```{r}
freq_kenya_error_mod_age <- glmer(is_far ~ condition*age_centered + (condition | child) + (condition | target_word),
              data = kenya_errors, family = "binomial")
summary(freq_kenya_error_mod_age)
```

Try a pruned model with age

```{r}
freq_kenya_error_mod_age_pruned <- glmer(is_far ~ condition*age_centered + (1| child) + (1 | target_word),
              data = kenya_errors, family = "binomial")
summary(freq_kenya_error_mod_age_pruned)

#more far errors in all three picture condiitons, relative to object condition - cool!
#interaction between age x bw

#get confidence intervals
cc <- confint(freq_kenya_error_mod_age_pruned,parm="beta_",method="Wald")
ctab <- cbind(est=fixef(freq_kenya_error_mod_age_pruned),cc)
rtab <- exp(ctab)
print(rtab,digits=3)
```


Run Bayesian version of Kenya error analysis, accounting for item effects - first without age

```{r}
kenya_error_mod <- brm(formula = is_far ~ condition + (condition | child) + (condition | target_word),
                 family=bernoulli(link="logit"), data = kenya_errors, seed = 1)

joint_tests(kenya_error_mod)

 #model term df1 df2 F.ratio  Chisq p.value
 #condition    3 Inf   6.508 19.524  0.0002

#effect of condition - cool
```

Get posterior estimates + 95% credible intervals

```{r}
kenya_error_mod%>%
  as_draws_df() %>%
  select(starts_with("b_")) %>% 
  mutate(obj = b_Intercept, 
         bw = b_Intercept + b_conditionbw, 
     	   cartoon = b_Intercept + b_conditioncartoon,
         photo = b_Intercept + b_conditionphoto) %>%
  select(obj, photo, cartoon, bw) %>%
  mean_hdi() %>%
  pivot_longer(cols = -c(.width:.interval),
               names_to = "index",
               values_to = "value") %>% 
  select(index, value) %>% 
  mutate(index = ifelse(str_detect(index, fixed(".")), index, str_c(index, ".mean"))) %>% 
  separate(index, into = c("parameter", "type"), sep = "\\.") %>% 
  pivot_wider(names_from = type, 
              values_from = value) %>%
  mutate_at(vars(2:4), plogis)

emmeans_kenya_error_mod <- kenya_error_mod%>% emmeans(specs = pairwise~condition)
summary(emmeans_kenya_error_mod)

```

Now run again with age

```{r}
kenya_error_mod_age <- brm(formula = is_far ~ condition*age_centered + (condition | child) + (condition | target_word),
                 family=bernoulli(link="logit"), data = kenya_errors, seed = 1)

joint_tests(kenya_error_mod_age)

 #model term             df1 df2 F.ratio  Chisq p.value
#condition                3 Inf   6.452 19.356  0.0002
#age_centered             1 Inf   2.158  2.158  0.1419
#condition:age_centered   3 Inf   2.165  6.495  0.0898

#main effect of condition - cool!
```

Get posterior estimates + 95% credible intervals

```{r}
kenya_error_mod_age %>%
  as_draws_df() %>%
  select(starts_with("b_")) %>% 
  mutate(obj = b_Intercept, 
         bw = b_Intercept + b_conditionbw, 
     	   cartoon = b_Intercept + b_conditioncartoon,
         photo = b_Intercept + b_conditionphoto) %>%
  select(obj, photo, cartoon, bw) %>%
  mean_hdi() %>%
  pivot_longer(cols = -c(.width:.interval),
               names_to = "index",
               values_to = "value") %>% 
  select(index, value) %>% 
  mutate(index = ifelse(str_detect(index, fixed(".")), index, str_c(index, ".mean"))) %>% 
  separate(index, into = c("parameter", "type"), sep = "\\.") %>% 
  pivot_wider(names_from = type, 
              values_from = value) %>%
  mutate_at(vars(2:4), plogis)

emmeans_kenya_error_mod_age <- kenya_error_mod_age%>% emmeans(specs = pairwise~condition)
summary(emmeans_kenya_error_mod_age)

#errors in all picture conditions different from object condition - credible intervals do not pass through zero
```

Visualize error analyses for both Kenya 

```{r}
kenya_respplot <- ggplot(kenya, aes(x = condition, fill = response_type)) +
        geom_bar(position = "fill") +
        facet_wrap(~floored_age, nrow = 1) +
        scale_y_continuous(labels = scales::percent) +
        labs(
         x = "condition",
         y = "proportion of responses",
         fill = "response type"
     ) +
      geom_hline(yintercept = 0.25, linetype = "dashed", color = "black") +
     theme_minimal() +
     theme(
       text = element_text(size = 14),          # Base text size
       axis.text = element_text(size = 12),     # Axis labels
       strip.text = element_text(size = 14),    # Facet labels
       legend.text = element_text(size = 12),    # Legend text
       aspect.ratio = 4,
       axis.text.x = element_text(angle = 90, hjust = 1)
     ) +
     scale_fill_brewer(palette="Dark2")

kenya_respplot
```

US error visualization

```{r}
us_respplot <- ggplot(us, aes(x = condition, fill = response_type)) +
        geom_bar(position = "fill") +
        facet_wrap(~floored_age, nrow = 1) +
        scale_y_continuous(labels = scales::percent) +
        labs(
         x = "condition",
         y = "proportion of responses",
         fill = "response type"
     ) +  
    geom_hline(yintercept = 0.25, linetype = "dashed", color = "black") +
     theme_minimal() +
     theme(
       text = element_text(size = 14),          # Base text size
       axis.text = element_text(size = 12),     # Axis labels
       strip.text = element_text(size = 14),    # Facet labels
       legend.text = element_text(size = 12),    # Legend text
       aspect.ratio = 4,
       axis.text.x = element_text(angle = 90, hjust = 1)
     ) +
     scale_fill_brewer(palette="Dark2")

us_respplot
 
```

Now Kenya error only

```{r}
kenya_errplot <- ggplot(kenya_errors, aes(x = condition, fill = response_type)) +
        geom_bar(position = "fill") +
        facet_wrap(~floored_age, nrow = 1) +
        scale_y_continuous(labels = scales::percent) +
        labs(
         x = "condition",
         y = "proportion of responses",
         fill = "response type"
     ) + 
  geom_hline(yintercept = 0.33, linetype = "dashed", color = "black") +
     theme_minimal() +
     theme(
       text = element_text(size = 14),          # Base text size
       axis.text = element_text(size = 12),     # Axis labels
       strip.text = element_text(size = 14),    # Facet labels
       legend.text = element_text(size = 12),    # Legend text
       aspect.ratio = 4,
       axis.text.x = element_text(angle = 90, hjust = 1)
     ) +
     scale_fill_brewer(palette="Dark2")

kenya_errplot
```


```{r}
us_errplot <- ggplot(us_errors, aes(x = condition, fill = response_type)) +
        geom_bar(position = "fill") +
        facet_wrap(~floored_age, nrow = 1) +
        scale_y_continuous(labels = scales::percent) +
        labs(
         x = "condition",
         y = "proportion of responses",
         fill = "response type"
     ) + 
  geom_hline(yintercept = 0.33, linetype = "dashed", color = "black") +
     theme_minimal() +
     theme(
       text = element_text(size = 14),          # Base text size
       axis.text = element_text(size = 12),     # Axis labels
       strip.text = element_text(size = 14),    # Facet labels
       legend.text = element_text(size = 12),    # Legend text
       aspect.ratio = 4,
       axis.text.x = element_text(angle = 90, hjust = 1)
     ) +
     scale_fill_brewer(palette="Dark2")

us_errplot
```

Run frequentist US models - full model without age (won't converge)

```{r}
freq_us_error_mod <- glmer(is_far ~ condition + (condition | child) + (condition | target_word),
              data = us_errors, family = "binomial")
summary(freq_us_error_mod)
#Error: number of observations (=139) < number of random effects (=220) for term (condition | child); the random-effects parameters are probably unidentifiable
```

How about a pruned model?

```{r}
freq_us_error_mod_pruned <- glmer(is_far ~ condition + (1 | child) + (1 | target_word),
              data = us_errors, family = "binomial")
summary(freq_us_error_mod_pruned)
#no difference between conditions!
```

Run frequentist US models - full model with age (won't converge)

```{r}
freq_us_error_mod_age <- glmer(is_far ~ condition*age_centered + (condition | child) + (condition | target_word),
              data = us_errors, family = "binomial")
summary(freq_us_error_mod_age)
#Error: number of observations (=139) < number of random effects (=220) for term (condition | child); the random-effects parameters are probably unidentifiable
```

First pruned model still won't converge

```{r}
freq_us_error_mod_age_pruned <- glmer(is_far ~ condition*age_centered + (1 | child) + (1 | target_word),
              data = us_errors, family = "binomial")
summary(freq_us_error_mod_age_pruned)
```
Prune again - remove item effects

```{r}
freq_us_error_mod_age_pruned2 <- glmer(is_far ~ condition*age_centered + (1 | child),
              data = us_errors, family = "binomial")
summary(freq_us_error_mod_age_pruned2)
#no effects of condition
```

Run the U.S. Bayesian version without age

```{r}
us_error_mod<- brm(formula = is_far ~ condition + (condition | child) + (condition | target_word),
                 family=bernoulli(link="logit"), data = us_errors, seed = 1)

joint_tests(us_error_mod)

# model term df1 df2 F.ratio Chisq p.value
#condition    3 Inf   0.403 1.209  0.7505

#no effect of condition
```
Get posterior estimates + 95% credible intervals

```{r}
us_error_mod%>%
  as_draws_df() %>%
  select(starts_with("b_")) %>% 
  mutate(obj = b_Intercept, 
         bw = b_Intercept + b_conditionbw, 
     	   cartoon = b_Intercept + b_conditioncartoon,
         photo = b_Intercept + b_conditionphoto) %>%
  select(obj, photo, cartoon, bw) %>%
  mean_hdi() %>%
  pivot_longer(cols = -c(.width:.interval),
               names_to = "index",
               values_to = "value") %>% 
  select(index, value) %>% 
  mutate(index = ifelse(str_detect(index, fixed(".")), index, str_c(index, ".mean"))) %>% 
  separate(index, into = c("parameter", "type"), sep = "\\.") %>% 
  pivot_wider(names_from = type, 
              values_from = value) %>%
  mutate_at(vars(2:4), plogis)

emmeans_us_error_mod <- us_error_mod%>% emmeans(specs = pairwise~condition)
summary(emmeans_us_error_mod)
```

Run the U.S. Bayesian version with age

```{r}
us_error_mod_age <- brm(formula = is_far ~ condition*age_centered + (condition | child) + (condition | target_word),
                 family=bernoulli(link="logit"), data = us_errors, seed = 1)

joint_tests(us_error_mod_age)

 #model term             df1 df2 F.ratio Chisq p.value
# condition                3 Inf   0.644 1.932  0.5869
# age_centered             1 Inf   0.850 0.850  0.3566
# condition:age_centered   3 Inf   1.662 4.986  0.1727

#no effect of condition in US Bayesian mod - also cooL!

```
Get posterior estimates + 95% credible intervals

```{r}
us_error_mod_age %>%
  as_draws_df() %>%
  select(starts_with("b_")) %>% 
  mutate(obj = b_Intercept, 
         bw = b_Intercept + b_conditionbw, 
     	   cartoon = b_Intercept + b_conditioncartoon,
         photo = b_Intercept + b_conditionphoto) %>%
  select(obj, photo, cartoon, bw) %>%
  mean_hdi() %>%
  pivot_longer(cols = -c(.width:.interval),
               names_to = "index",
               values_to = "value") %>% 
  select(index, value) %>% 
  mutate(index = ifelse(str_detect(index, fixed(".")), index, str_c(index, ".mean"))) %>% 
  separate(index, into = c("parameter", "type"), sep = "\\.") %>% 
  pivot_wider(names_from = type, 
              values_from = value) %>%
  mutate_at(vars(2:4), plogis)

emmeans_us_error_mod_age <- us_error_mod_age%>% emmeans(specs = pairwise~condition)
summary(emmeans_us_error_mod_age)

```

Differences in errors across contexts?

```{r}
all_errors <- error_d %>%
    filter(response_type %in% c("near","far")) %>% 
    mutate(is_far = response_type=="far")

full_mod <- glmer(
     is_far ~ context*condition*age + (1 | child) + (1 | target_word), 
     data=all_errors, 
     family = "binomial")
summary(full_mod)
#model doesn't converge

full_mod <- glmer(
     is_far ~ context*condition + age + (1 | child) + (1 | target_word), 
     data=all_errors, 
     family = "binomial")
summary(full_mod)

full_mod_no_interaction <- glmer(
     is_far ~ context+condition + age + (1 | child) + (1 | target_word), 
     data=all_errors, 
     family = "binomial")
summary(full_mod_no_interaction)

```


Running exploratory individual differences analyses - effect of picture experience on accuracy. Start with a bare model without control variables

```{r}
mod_bare <- glmer(accuracy ~ pic_interact * condition + (condition | child) + (condition | target_word),
              data = d, family = "binomial")
summary(mod_bare)
#doesn't converge
```

Try a pruned bare model

```{r}
mod_bare_pruned <- glmer(accuracy ~ pic_interact * condition + (1 | child) + (1 | target_word),
              data = d, family = "binomial")
summary(mod_bare_pruned)
#no effects
```

What about a model with control variables?

```{r}
mod_full <- glmer(accuracy ~ pic_interact * condition + play + talk + toy_num + maternal_ed + (condition | child) + (condition | target_word),
              data = d, family = "binomial")
summary(mod_full)
#this doesn't converge either
```

Pruned version of the model with control variables?

```{r}
mod_full_pruned <- glmer(accuracy ~ pic_interact * condition + play + talk + toy_num + maternal_ed + (1| child) + (1 | target_word),
              data = d, family = "binomial")
summary(mod_full_pruned)
#this also fails to converge
```

Prune the full model further

```{r}
mod_full_pruned2 <- glmer(accuracy ~ pic_interact * condition + play + talk + toy_num + maternal_ed + (1| child),
              data = d, family = "binomial")
summary(mod_full_pruned2)
#model still not converging
```

Continue pruning!

```{r}
mod_full_pruned3 <- glm(accuracy ~ pic_interact * condition + play + talk + toy_num + maternal_ed,
              data = d, family = "binomial")
summary(mod_full_pruned3)
#no effects
```

Now try it with the two-factor variables (kid items and wall items)? Start with the bare model

```{r}
mod_bare_factor <- glmer(accuracy ~ kid_items * wall_items * condition + (condition | child) + (condition | target_word),
              data = d, family = "binomial")
summary(mod_bare_factor)
#doesn't converge
```

Prune for convergence

```{r}
mod_bare_factor_pruned <- glmer(accuracy ~ kid_items * wall_items * condition + (1 | child) + (1 | target_word),
              data = d, family = "binomial")
summary(mod_bare_factor_pruned)
#still doesn't converge
```

Keep pruning

```{r}
mod_bare_factor_pruned2 <- glmer(accuracy ~ kid_items * wall_items * condition + (1 | child),
              data = d, family = "binomial")
summary(mod_bare_factor_pruned2)
#still not converging
```

Keep pruning...

```{r}
mod_bare_factor_pruned3 <- glm(accuracy ~ kid_items * wall_items * condition,
              data = d, family = "binomial")
summary(mod_bare_factor_pruned3)
#nothing significant except main effect of object type
```

Now with the full model

```{r}

mod_full_pruned_factor <- glm(accuracy ~ kid_items * wall_items * condition + play + talk + toy_num + maternal_ed,
              data = d, family = "binomial")
summary(mod_full_pruned_factor)
#still nothing
```





```{r}
mod_pic <- glmer(accuracy ~ pic_interact * condition + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = d, family = "binomial")
summary(mod_pic)
#all null effects

mod_pic_age <- glmer(accuracy ~ pic_interact * age_centered * condition + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = d, family = "binomial")
summary(mod_pic_age)
#model failed to converge

mod_pic_age_pruned <- glm(accuracy ~ pic_interact * age_centered * condition + play + talk + toy_num + maternal_ed,
              data = d, family = "binomial")
summary(mod_pic_age_pruned)
#main effect of age and nothing else

#now run the analyses on only picture conditions (remove object condition)

mod_pic_age <- glm(accuracy ~ pic_interact * age_centered * condition + play + talk + toy_num + maternal_ed,
              data = d, family = "binomial")
summary(mod_pic_age)
#no effects in pruned model


library(dplyr)
agg <- group_by(d, super_condition)
pic_condition <- subset(agg, super_condition == "pic")

mod_pic_only <- glmer(accuracy ~ pic_interact * condition + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = pic_condition, family = "binomial")
summary(mod_pic_only)
#all null effects

mod_pic_only_age <- glmer(accuracy ~ pic_interact * condition * age_centered + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = pic_condition, family = "binomial")
summary(mod_pic_only_age)
#main effect of age, but pic interaction x age effect goes away...

```

Running exploratory individual differences analyses - effect of picture experience on accuracy - separated by condition

```{r}
library(dplyr)
agg1 <- group_by(d, condition)
obj <- subset(agg1, condition == "obj")
photo <- subset(agg1, condition == "photo")
cartoon <- subset(agg1, condition == "cartoon")
bw <- subset(agg1, condition == "bw")

mod_obj <- glmer(accuracy ~ pic_interact + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = obj, family = "binomial")
summary(mod_obj)

mod_obj_age <- glmer(accuracy ~ pic_interact * age_centered + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = obj, family = "binomial")
summary(mod_obj_age)
#age x pic interaction effect

mod_photo <- glmer(accuracy ~ pic_interact + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = photo, family = "binomial")
summary(mod_photo)

mod_photo_age <- glmer(accuracy ~ pic_interact * age_centered + play + talk + toy_num + maternal_ed +  (1 | target_word),
              data = photo, family = "binomial")
summary(mod_photo_age)

mod_cartoon <- glmer(accuracy ~ pic_interact + play + talk + toy_num + maternal_ed +  (1 | target_word),
              data = cartoon, family = "binomial")
summary(mod_cartoon)

mod_cartoon_age <- glmer(accuracy ~ pic_interact * age_centered + play + talk + toy_num + maternal_ed +  (1 | target_word),
              data = cartoon, family = "binomial")
summary(mod_cartoon_age)
#failed to converge

mod_bw <- glmer(accuracy ~ pic_interact + play + talk + toy_num + maternal_ed +  (1 | target_word),
              data = bw, family = "binomial")
summary(mod_bw)

mod_bw_age <- glmer(accuracy ~ pic_interact * age_centered + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = bw, family = "binomial")
summary(mod_bw_age)

```
```{r}

```

Some data viz

```{r}
#plot all data

ms2 <- d |>
  group_by(child, condition, age, pic_interact, pic_num) |>
  summarise(accuracy = mean(accuracy))

ggplot(ms2, aes(x=pic_interact, y = accuracy, col = condition)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Interact with Picture Books")

ms_obj <- obj |>
  group_by(child, condition, age, pic_interact, pic_num) |>
  summarise(accuracy = mean(accuracy))

ms_photo <- photo |>
  group_by(child, condition, age, pic_interact, pic_num) |>
  summarise(accuracy = mean(accuracy))

ms_cartoon <- cartoon |>
  group_by(child, condition, age, pic_interact, pic_num) |>
  summarise(accuracy = mean(accuracy))

ms_bw <- bw |>
  group_by(child, condition, age, pic_interact, pic_num) |>
  summarise(accuracy = mean(accuracy))

obj_plot <- ggplot(ms_obj, aes(x=pic_interact, y = accuracy, col = age)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Pic Interaction Freq") +
  theme(legend.position = "bottom") +
  ggtitle("Objects") +
  ylim(0,1)

photo_plot <- ggplot(ms_photo, aes(x=pic_interact, y = accuracy, col = age)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Pic Interaction Freq") +
  theme(legend.position = "bottom") +
  ggtitle("Photographs") +
  ylim(0,1)

cartoon_plot <- ggplot(ms_cartoon, aes(x=pic_interact, y = accuracy, col = age)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Pic Interaction Freq") +
  theme(legend.position = "bottom") +
  ggtitle("Cartoons") +
  ylim(0,1)

bw_plot <- ggplot(ms_bw, aes(x=pic_interact, y = accuracy, col = age)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Pic Interaction Freq") +
  theme(legend.position = "bottom") +
  ggtitle("B&W Drawings") +
  ylim(0,1)

require(gridExtra)
grid.arrange(obj_plot, photo_plot, cartoon_plot, bw_plot, ncol=4)

```

More data viz with a different picture experience variable - i.e., number of picture books in the home

```{r}
obj_plot2 <- ggplot(ms_obj, aes(x=pic_num, y = accuracy, col = age)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Pic Book Number") +
  theme(legend.position = "bottom") +
  ggtitle("Obj") +
  ylim(0,1)

photo_plot2 <- ggplot(ms_photo, aes(x=pic_num, y = accuracy, col = age)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Pic Book Number") +
  theme(legend.position = "bottom") +
  ggtitle("Photo") +
  ylim(0,1)

cartoon_plot2 <- ggplot(ms_cartoon, aes(x=pic_num, y = accuracy, col = age)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Pic Book Number") +
  theme(legend.position = "bottom") +
  ggtitle("Cartoon") +
  ylim(0,1)

bw_plot2 <- ggplot(ms_bw, aes(x=pic_num, y = accuracy, col = age)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Pic Book Number") +
  theme(legend.position = "bottom") +
  ggtitle("Bw") +
  ylim(0,1)

require(gridExtra)
grid.arrange(obj_plot2, photo_plot2, cartoon_plot2, bw_plot2, ncol=4)
```


Can rerun these analyses with a different picture experience variable - i.e., number of picture books in the home

```{r}
mod_pic_num <- glmer(accuracy ~ pic_num * condition + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = d, family = "binomial")
summary(mod_pic_num)
#all null effects

mod_pic_num_age <- glmer(accuracy ~ pic_num * condition * age_centered + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = d, family = "binomial")
summary(mod_pic_num_age)
#large main effect of age
#nothing else

#now run the analyses on only picture conditions (remove object condition)

library(dplyr)
agg <- group_by(d, super_condition)
pic_condition <- subset(agg, super_condition == "pic")

mod_pic_num_only <- glmer(accuracy ~ pic_num * condition + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = pic_condition, family = "binomial")
summary(mod_pic_num_only)
#all null effects

mod_pic_num_only_age <- glmer(accuracy ~ pic_num * condition * age_centered + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = pic_condition, family = "binomial")
summary(mod_pic_num_only_age)
#effect of photo condition and age?
```

Can rerun these analyses with a different picture experience variable - i.e., number of picture books in the home - separated by condition

```{r}

#all null
#except for main effect of age

mod_obj_num <- glmer(accuracy ~ pic_num + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = obj, family = "binomial")
summary(mod_obj_num)

mod_obj_num_age <- glmer(accuracy ~ pic_num * age_centered + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = obj, family = "binomial")
summary(mod_obj_num_age)
#age x pic interaction effect

mod_photo_num <- glmer(accuracy ~ pic_num + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = photo, family = "binomial")
summary(mod_photo_num)

mod_photo_num_age <- glmer(accuracy ~ pic_num * age_centered + play + talk + toy_num + maternal_ed +  (1 | target_word),
              data = photo, family = "binomial")
summary(mod_photo_num_age)

mod_cartoon_num <- glmer(accuracy ~ pic_num + play + talk + toy_num + maternal_ed +  (1 | target_word),
              data = cartoon, family = "binomial")
summary(mod_cartoon_num)

mod_cartoon_num_age <- glmer(accuracy ~ pic_num * age_centered + play + talk + toy_num + maternal_ed +  (1 | target_word),
              data = cartoon, family = "binomial")
summary(mod_cartoon_num_age)

mod_bw_num <- glmer(accuracy ~ pic_num + play + talk + toy_num + maternal_ed +  (1 | target_word),
              data = bw, family = "binomial")
summary(mod_bw_num)

mod_bw_num_age <- glmer(accuracy ~ pic_num * age_centered + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = bw, family = "binomial")
summary(mod_bw_num_age)

```

Full Bayesian model for exploratory analyses?

```{r}
#keep getting errors in the bayesian models
#Error in solve.default(zcov, z) : 
#system is computationally singular: reciprocal condition number = 3.5628e-17

bayes_mod_pic <- brm(formula = accuracy ~ pic_interact + play + talk + toy_num + maternal_ed + (condition | target_word),
                 family=bernoulli(link="logit"), data = d, seed = 1)

joint_tests(bayes_mod_pic)

bayes_mod_pic_only <- brm(formula = accuracy ~ pic_interact + play + talk + toy_num + maternal_ed + (condition | target_word),
                 family=bernoulli(link="logit"), data = pic_condition, seed = 1)

joint_tests(bayes_mod_pic_only)
```

# Factor analysis

Exploratory factor analysis on caregiver questionnaire variables

```{r}

d2 <- select(d, pic_interact, pic_num, draw_num, poster_num, tv_num) 

ev <- eigen(cor(d2)) # get eigenvalues
ev$values

scree(d2, pc=FALSE) 

fa.parallel(d2, fa="fa")
#Parallel analysis suggests that the number of factors =  3  and the number of components =  NA 
#but fit 2 factors because 3 factors are too many for 5 variables

#assume correlation between variables
Nfacs <- 2
fit <- factanal(d2, Nfacs, rotation="promax")
print(fit, digits=2, cutoff=0.3, sort=TRUE)

#Loadings:
#             Factor1 Factor2
#draw_num      1.00          
#poster_num            0.87  
#pic_interact          0.32  
#pic_num       0.36          
#tv_num                0.34  

#assume independence between variables
Nfacs <- 2
fit <- factanal(d2, Nfacs, rotation="varimax")
print(fit, digits=2, cutoff=0.3, sort=TRUE)

#Loadings:
#             Factor1 Factor2
#draw_num     1.00           
#poster_num           0.83   
#pic_interact                
#pic_num      0.40           
#tv_num               0.32   

```

Confirmatory factor analysis

```{r}
all_mod <- 'all_items =~ draw_num + pic_num + poster_num + tv_num + pic_interact'
num_mod <- 'num_items =~ draw_num + pic_num + poster_num + tv_num'

all_fit <- cfa(all_mod, data = d2)
summary(all_fit, fit.measures = TRUE)
#RMSEA = 0.159

num_fit <- cfa(num_mod, data = d2)
summary(num_fit, fit.measures = TRUE)
#RMSEA = 0.182

#get alphas too
 
psych::alpha(d2[c("draw_num", "pic_num", "poster_num", "tv_num")])
 
psych::alpha(d2)

two_mod <- 'kid_items =~ draw_num + pic_num
            wall_items =~ poster_num + tv_num'

two_fit <- cfa(two_mod, data = d2)
summary(two_fit, fit.measures = TRUE)

psych::alpha(d2[c("draw_num", "pic_num")])
psych::alpha(d2[c("poster_num", "tv_num")])

#two factor model isn't great either though

```

Histograms of variable distributions

```{r}

ggplot(d2, aes(x = pic_interact)) + 
  geom_histogram(binwidth = 1)

ggplot(d2, aes(x = pic_num)) + 
  geom_histogram(binwidth = 1)

ggplot(d2, aes(x = draw_num)) + 
  geom_histogram(binwidth = 1)

ggplot(d2, aes(x = poster_num)) + 
  geom_histogram(binwidth = 1)

ggplot(d2, aes(x = tv_num)) + 
  geom_histogram(binwidth = 1)


```

Log transform and z-score variables

```{r}
log_draw_num <- log(d2$draw_num+.01)
log_poster_num <- log(d2$poster_num+.01)
log_pic_num <- log(d2$pic_num+.01)

z_log_draw_num <- (log_draw_num - mean(log_draw_num))/sd(log_draw_num)
z_log_poster_num <- (log_poster_num - mean(log_poster_num))/sd(log_poster_num)
z_log_pic_num <- (log_pic_num - mean(log_pic_num))/sd(log_pic_num)
z_pic_interact <-(d2$pic_interact - mean(d2$pic_interact))/sd(d2$pic_interact)
z_tv_num <-(d2$tv_num - mean(d2$tv_num))/sd(d2$tv_num)

```

Repeat factor analyses with z-scored variables

```{r}

d3 <- data.frame(z_log_draw_num, z_log_poster_num, z_log_pic_num, z_pic_interact, z_tv_num)

ev <- eigen(cor(d3)) # get eigenvalues
ev$values
#2 factors are sufficient

fa.parallel(d3, fa="fa")
#Parallel analysis suggests that the number of factors =  0 (??)  and the number of components =  NA 

#assume correlation between variables
Nfacs <- 2
fit <- factanal(d3, Nfacs, rotation="promax")
print(fit, digits=2, cutoff=0.3, sort=TRUE)

#Loadings:
#                 Factor1 Factor2
#z_log_draw_num    1.01          
#z_log_poster_num          0.74  
#z_log_pic_num                   
#z_pic_interact            0.34  
#z_tv_num    

#assume independence between variables
Nfacs <- 2
fit <- factanal(d3, Nfacs, rotation="varimax")
print(fit, digits=2, cutoff=0.3, sort=TRUE)

#Loadings:
#                 Factor1 Factor2
#z_log_draw_num   1.00           
#z_log_poster_num         0.72   
#z_log_pic_num                   
#z_pic_interact           0.33   
#z_tv_num           

```

Confirmatory Analyses

```{r}

z_all_mod <- 'all_items =~ z_log_draw_num + z_log_poster_num + z_log_pic_num + z_tv_num + z_pic_interact'
z_num_mod <- 'num_items =~ z_log_draw_num + z_log_poster_num + z_log_pic_num + z_tv_num'

z_all_fit <- cfa(z_all_mod, data = d3)
summary(z_all_fit, fit.measures = TRUE)
#RMSEA = 0.079

z_num_fit <- cfa(z_num_mod, data = d3)
summary(z_num_fit, fit.measures = TRUE)
#RMSEA = 0.072

#get alphas too
 
psych::alpha(d3[c("z_log_draw_num", "z_log_pic_num", "z_log_poster_num", "z_tv_num")])
 
psych::alpha(d3)


# two_mod <- 'kid_items =~ draw_num + pic_num
#             wall_items =~ poster_num + tv_num'

z_two_mod <- 'kid_items =~ z_log_draw_num + z_log_pic_num
            wall_items =~ z_log_poster_num + z_tv_num'

z_two_fit <- cfa(z_two_mod, data = d3)
summary(z_two_fit, fit.measures = TRUE)

psych::alpha(d3[c("z_log_poster_num", "z_tv_num")])

two_factor <- predict(z_two_fit)

```

Run exploratory analysis with two factors

```{r}
mod_two_factor <- glmer(accuracy ~ kid_items * wall_items * age_centered * condition + play + talk + toy_num + maternal_ed + (1 | child),
              data = d, family = "binomial")
summary(mod_two_factor)



```

Do exploratory analyses with one-factor loading for Kenya kids?

```{r}
mod_pic_total <- glmer(accuracy ~ z_total * condition + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = d, family = "binomial")
summary(mod_pic_total)
#main effect of bw, no effect of picture experience

mod_pic_total_age <- glmer(accuracy ~ z_total * condition * age_centered + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = d, family = "binomial")
summary(mod_pic_total_age)
#main effect of age and bw condition
#marginal effect of picture experience, p = .08
```

Run the analyses on only picture conditions (remove object condition)

```{r}
agg <- group_by(d, super_condition)
obj_condition <- subset(agg, super_condition == "obj")
pic_condition <- subset(agg, super_condition == "pic")

mod_pic_total_only <- glmer(accuracy ~ z_total * condition + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = pic_condition, family = "binomial")
summary(mod_pic_total_only)
#cartoon and photo more accurate than black and white

mod_pic_total_age_only <- glmer(accuracy ~ z_total * condition * age_centered  + play + talk + toy_num + maternal_ed + (1 | target_word),
              data = pic_condition, family = "binomial")
summary(mod_pic_total_age_only)
#effect of condition and age
```

Some data viz

```{r}
obj_plot3 <- ggplot(obj_condition, aes(x=pic_num, y = accuracy, col = age)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Pic Experience Sum Score") +
  theme(legend.position = "bottom") +
  ggtitle("Obj") +
  ylim(0,1)

pic_plot3 <- ggplot(pic_condition, aes(x=pic_num, y = accuracy, col = age)) + 
  geom_jitter(alpha = .5, height = .02, width = 0) + 
  geom_smooth(method = "lm") + 
  ylab("Accuracy") +
  xlab("Pic Experience Sum Score") +
  theme(legend.position = "bottom") +
  ggtitle("Obj") +
  ylim(0,1)
  
```

