---
title: "picture-perception-error-analysis"
author: "Arnav Verma"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lme4)
library(ggplot2)
```

## Load in data
* Do a little bit of cleanup
* Set the object condition to be the reference level
* Also apply age binning

```{r}
trialdata <- read_csv('data/all_df.csv') %>% select(-"Unnamed: 0")

trialdata$condition <- relevel(factor(trialdata$condition), ref = "obj") # set object to the reference level

trialdata <- trialdata %>% 
              mutate(rounded_age = factor(round(age))) %>% # bin age in two ways 
              mutate(floored_age = factor(floor(age))) %>%
              mutate(response_type = fct_recode(response_type, # also recode response type
                                   "near" = "Near Distractor",
                                   "far" = "Random",
                                   "target" = "Target")) %>%
              mutate(response_type = factor(response_type,
                                            levels = c("far", "near","target"),
                                            ordered = TRUE)) %>%
              mutate(condition = fct_recode(factor(condition), # recode condition and set levels
                                 "monochrome" = "bw",
                                 "object" = "obj",
                                 "photo" = "photo",
                                 "cartoon" = "cartoon")) %>% 
              mutate(condition = factor(condition,
                                        levels = c("object", "photo","cartoon", "monochrome"),
                                        ordered = FALSE))


trialdata$condition <- relevel(factor(trialdata$condition), ref = "object") # set object to the reference level

```

## Visualizing variation in ALL response types across conditions, and broken out by age

```{r}
respplot <- ggplot(trialdata, aes(x = condition, fill = response_type)) +
        geom_bar(position = "fill") +
        facet_wrap(~floored_age, nrow = 1) +
        scale_y_continuous(labels = scales::percent) +
        labs(
         x = "condition",
         y = "proportion of responses",
         fill = "response type"
     ) +
     theme_minimal() +
     theme(
       text = element_text(size = 14),          # Base text size
       axis.text = element_text(size = 12),     # Axis labels
       strip.text = element_text(size = 14),    # Facet labels
       legend.text = element_text(size = 12),    # Legend text
       aspect.ratio = 4,
       axis.text.x = element_text(angle = 90, hjust = 1)
     ) +
     scale_fill_brewer(palette="Dark2")

respplot

## use this bit to control how figure image is saved to disk
ggsave('paper/figs/response_type_by_condition_and_age.pdf',
       plot = respplot, device = "pdf",
       width = 12, height = 6, useDingbats = FALSE)
```

## Visualizing variation in ONLY ERRONEOUS responses across conditions, and broken out by age

```{r}
errors <- trialdata %>%
    filter(response_type %in% c("near","far")) %>% 
    mutate(is_far = response_type=="far")
 
errplot <- ggplot(errors, aes(x = condition, fill = response_type)) +
        geom_bar(position = "fill") +
        facet_wrap(~floored_age, nrow = 1) +
        scale_y_continuous(labels = scales::percent) +
        labs(
         x = "condition",
         y = "proportion of responses",
         fill = "response type"
     ) + 
  geom_hline(yintercept = 0.33, linetype = "dashed", color = "black") +
     theme_minimal() +
     theme(
       text = element_text(size = 14),          # Base text size
       axis.text = element_text(size = 12),     # Axis labels
       strip.text = element_text(size = 14),    # Facet labels
       legend.text = element_text(size = 12),    # Legend text
       aspect.ratio = 4,
       axis.text.x = element_text(angle = 90, hjust = 1)
     ) +
     scale_fill_brewer(palette="Dark2")

errplot

## use this bit to control how figure image is saved to disk
ggsave('paper/figs/error_type_by_condition_and_age.pdf',
       plot = errplot, device = "pdf",
       width = 12, height = 6, useDingbats = FALSE)
```


## Evaluating effect of condition on type of error (far vs. near)

First attempt uses well motivated but complex random-effects structure. Convergence issues. Commented out because it is painful to watch/wait for this one.

```{r}
# base_model <- glmer(
#     is_far ~ 1  + (condition | child) + (condition * floored_age | target_word), 
#     data=errors, 
#     family = "binomial"
# )
# 
# condition_model <- glmer(
#     is_far ~ condition * age + (condition | child) + (condition * floored_age | target_word), 
#     data=errors, 
#     family = "binomial"
# )

```

Second attempt uses simpler random-effects structure. Still there are convergence issues.

```{r}
base_model <- glmer(
    is_far ~ 1  + (condition | child) + (1 | target_word), 
    data=errors, 
    family = "binomial"
)

condition_model <- glmer(
     is_far ~ condition + (condition | child) + (1 | target_word), 
     data=errors, 
     family = "binomial"
)

anova(base_model, condition_model, test = "Chisq")
```

Third attempt uses even simpler random-effects structure. Now we get convergence.

```{r}
base_model <- glmer(
    is_far ~ 1  + (1 | child) + (1| target_word), 
    data=errors, 
    family = "binomial"
)

condition_model <- glmer(
     is_far ~ condition + (1 | child) + (1| target_word), 
     data=errors, 
     family = "binomial"
)

```


Now let's get a little more ambitious and add age in as a fixed effect, with the interaction
```{r}
age_condition_model <- glmer(
     is_far ~ condition*age + (1 | child) + (1 | target_word), 
     data=errors, 
     family = "binomial"
)

age_condition_model_nointeraction <- glmer(
     is_far ~ condition + age + (1 | child) + (1 | target_word), 
     data=errors, 
     family = "binomial"
)
```

Summary of `age` * `condition` model

```{r}
summary(age_condition_model)
```

Summary of `condition` only model
```{r}
summary(condition_model)
```


Test for reliability of effect of condition and age
```{r}
anova(base_model, condition_model, age_condition_model)
```

