---
title: "picture-perception-error-analysis"
author: "Arnav Verma"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lme4)
library(ggplot2)
```

## Load in error trial-only dataframe created in `incorrect_analysis.ipynb` and take a peek
* `is_random`: TRUE if the far distractor was chosen; FALSE otherwise
* `condition`: stimulus presentation modality

```{r}
errors <- read_csv('data_processing/all_selection_df.csv')
errors$condition <- relevel(factor(errors$condition), ref = "object") # set object to the reference level
head(errors)
```


## Evaluating effect of condition on type of error (far vs. near)

First attempt uses well motivated but complex random-effects structure. Convergence issues. Commented out because it is painful to watch/wait for this one.

```{r}
# base_model <- glmer(
#     is_random ~ 1  + (condition | child) + (condition * age | target_word), 
#     data=errors, 
#     family = "binomial"
# )
# 
# condition_model <- glmer(
#     is_random ~ condition * age + (condition | child) + (condition * age | target_word), 
#     data=errors, 
#     family = "binomial"
# )

```

Second attempt uses simpler random-effects structure. Still there are convergence issues.

```{r}
base_model <- glmer(
    is_random ~ 1  + (condition | child), 
    data=errors, 
    family = "binomial"
)

condition_model <- glmer(
     is_random ~ condition + (condition | child), 
     data=errors, 
     family = "binomial"
)

anova(base_model, condition_model, test = "Chisq")
```
Third attempt uses even simpler random-effects structure. Now we get convergence.

```{r}
base_model <- glmer(
    is_random ~ 1  + (1 | child), 
    data=errors, 
    family = "binomial"
)

condition_model <- glmer(
     is_random ~ condition + (1 | child), 
     data=errors, 
     family = "binomial"
)

```
Summary of condition model
```{r}
summary(condition_model)
```


Test for reliability of effect of condition
```{r}
anova(base_model, condition_model, test = "Chisq")
```

